Rates of true polar wander in convecting planets

### 2015-09-08 tpw_rate.tex
fix

\begin{equation}
\frac{\partial T}{\partial t} + {\bf u} \cdot \nabla T = \kappa \nabla^2 T
\label{eq:energy}
\end{equation}
where $\bf u$ is the velocity, $P$ is the pressure, and $T$ is the temperature
(see Table~\ref{tab:parameters} for definitions of the other parameters}.
In addition we use the simple equation of state
\begin{equation}
\rho = \rho_0 \left( 1 - \alpha (T-T_0) \right)
\label{eq:eos}
\end{equation}
The other parameters are defined in Table \ref{tab:parameters}.
Note that here we retain the centrifugal term, which is normally either neglected or absorbed into a modified pressure.
Dimensional analysis of this system (cf. \citet{barenblatt1996scaling}) requires four nondimensional numbers to characterize it
(a fifth one, defined by the ratio of the length of day to a diffusion timescale, does not appear in the governing equations).
Convenient choices for these numbers are listed in Table \ref{tab:nondim}, along with approximate Earth-like values for them.

>>>>

\begin{equation}
\frac{\partial T}{\partial t} + {\bf u} \cdot \nabla T = \kappa \nabla^2 T
\label{eq:energy}
\end{equation}
where $\bf u$ is the velocity, $P$ is the pressure, and $T$ is the temperature
(see Table~\ref{tab:parameters} for definitions of the other parameters).
In addition we use the simple equation of state
\begin{equation}
\rho = \rho_0 \left( 1 - \alpha (T-T_0) \right)
\label{eq:eos}
\end{equation}
The other parameters are defined in Table \ref{tab:parameters}.
Note that here we retain the centrifugal term, which is normally either neglected or absorbed into a modified pressure.
Dimensional analysis of this system (cf. \citet{barenblatt1996scaling}) requires four nondimensional numbers to characterize it
(a fifth one, defined by the ratio of the length of day to a diffusion timescale, does not appear in the governing equations).
Convenient choices for these numbers are listed in Table \ref{tab:nondim}, along with approximate Earth-like values for them.
